---
title: "Emily’s Respiration and Breakdown Data"
author: "Emily Huff and James Wood"
date: "July 15, 2020"
output: html_document
---

Starting here - 

Loading data files for the whole data set and for the NO AMD (including no Crap Stream)

```{r}


microdfa <- read.csv("Emily Data.csv")

# this removed a big outlier data point (365) - a respiraton measurement of 8 (woodsdale creek) when rest were ~1 or 2. Will need to recalculate Site average if used. Also removed  (319) which had a resp about double the others at the Site. 
microdf<-microdfa[-c(103,243,319,346, 348, 365), ]


spongedf <- subset(microdf, Substrate=="Cellulose Sponge" & Week.Removed==4)
wooddf4 <- subset(microdf, Substrate=="Wood Veneer" & Week.Removed==4)
wooddf6 <- subset(microdf, Substrate=="Wood Veneer" & Week.Removed==6)

```

Instead of using this new CSV, I'm going to just make a new matrix that is based on microdf but with the AMD and CS in it

No AMD sites
```{r}
micronoamdCS<-microdf[-c(65:126, 224:253),]

spongenoamdCS <- subset(micronoamdCS, Substrate=="Cellulose Sponge" & Week.Removed==4)
woodnoamdCS <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==6)
woodnoamdCS.4 <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==4)
```


Loading Libraries
```{r}
library(lme4)
library(ggplot2)
library(ggmap)
library(AICcmodavg)
library(scatterplot3d)
library(devtools)
library(cowplot)
library(MuMIn)
library(usdm)
```

Looking for colinearity in the predictor variables using VIFSTEP function.

Result: VIF score indicates DIN and conductivity has a collinearity problem,
and need to be removed from the data set if used in conjunction with other variables. We can still use them indicidually. 
```{r}
cs1 <- data.frame(scale(microdf$Conductivity),
                  scale(microdf$H),
                  scale(microdf$DO),
                  scale(microdf$Turbidity),
                  scale(microdf$Temp),
                  scale(microdf$Chloride),
                  scale(microdf$SRP),
                  scale(microdf$Nitrate),
                  scale(microdf$Ammonium),
                  scale(microdf$DIN))
cs2 <- vifstep(cs1, th = 10)
cs2
```



## This will plot the x~y relationship of all the variables. 

Result: From looking at these gaphs you can see why the conductivity and DIN were removed. DIN appears to be strongly correlated with Nitrate and Ammonia - this is expected, and Conductivity and Chloride appear to be correlated. This would be expected also. DIN and Conductivity also appear to correlated with other variables. 
```{r}
pairs(~Conductivity+    H+     DO+ Turbidity+ Temp+    Chloride+      SRP+      Nitrate+         +       Ammonium+      DIN, data=spongedf)
```

Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 


Becase we only have 13 Sites in the whole data set we will later remove the AMD impacted Sites we only have 10 Sites, we really should limit the number of predictors in our model. Ideally you have at least 10 Sites for each predcitors. This is often unrealistic, but we'll limit ourselves to models with two or less predictor variables just to be a bit conservative. If need be, we can also reduce it further)

 

# Using a more limited set of models so that we are not overfitting
# This is the same set of models (i.e. water chemistry predictors) that were
# chosen to use with the sponge data. 



######################################################################################
##                        Sponge Models
#####################################################################################

Models for Respiration on Sponge substrates

#####################################################################################
#####################################################################################

I added turbidity, DO, and H to the model choices. Also I changed the random effect to Site so that we are modeling in a way that says there is variation in each Site. If we don't do it that way, then we would need to get a Site average of respiration instead of individual respiration.



## AICc Results for Sponge for all the sites
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 35 5 121.23       0.00   0.94   0.94 -54.93
model 17 5 129.19       7.96   0.02   0.96 -58.91
model 11 4 131.37      10.14   0.01   0.96 -61.24

: Note there are some errors in running these models that not all of them converged, which I will need to look into what's going on. 

```{r}
bResp2.models<-list()
bResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)




## Creating a vector of names to trace back models in set
bModnamesResp2 <- paste("model", 1:length(bResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = bResp2.models, modnames = bModnamesResp2, sort = TRUE)
```
 
## Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 
 
 Results:
           R2m       R2c
[35] 0.6198154 0.8030915
           R2m       R2c
[17] 0.4218287 0.8048477
           R2m      R2c
[11] 0.2275871 0.802891

```{r}
r.squaredGLMM(bResp2.models[[35]])
r.squaredGLMM(bResp2.models[[17]])
r.squaredGLMM(bResp2.models[[11]])
```

Lastly we see how big of an effect our predictor variables have on respiration rate. 
From Model 35

#                    2.5 %     97.5 %
.sig01           0.3293433  0.9692943
.sigma           0.4817444  0.7637504
(Intercept)      1.3644220  2.1294752
scale(H)        -2.0319719 -0.7576644
scale(Chloride)  1.1044317  2.3789479

```{r}
confint(bResp2.models[[35]])
confint(bResp2.models[[17]])
confint(bResp2.models[[11]])

summary(bResp2.models[[35]])

plot(spongedf$H ~ spongedf$Chloride)
plot(spongedf$RespRateInd ~ spongedf$Chloride)
plot(spongedf$RespRateInd ~ spongedf$H)
```



Conclusion for Sponge Models: 
The only model that had much support was H + Chloride and we have a nice mR2 value, indicating that we were able to explain 62% of the variation in the data with this model. 
If you plot choloride and H .. plot (Chloride~H, data=spongedf) .. you can see that we have this one really low pH Site (high H) with a big difference between it and the other Sites, AND it is our really high chloride Site. 


<<<<<<< HEAD
## Sponge Averages for breakdown vs resp

```{r}
mean.resp.sponge<-tapply(spongedf$RespRateInd, spongedf$Site, mean)
mean.break.sponge<-tapply(spongedf$Breakdown, spongedf$Site, mean)

summary(lm(mean.break.sponge~mean.resp.sponge))


#From Usher     
#cellulose_data$carbon_loss=((cellulose_data$Initial_wt)-(cellulose_data$c_afdm))*.30


#cellulose_data$mg_o2=cellulose_data$c_res*24*cellulose_data$c_afdm#mg O2 respired per day (no longer normalized by AFDM)

#cellulose_data$g_carbon_resp=((cellulose_data$c_res*.85*(12/32))/.3)/100###convert to g/C respired/day

#cellulose_data$c_resp_cafdm=((cellulose_data$c_res*.85*(12/32))/.3)*24#mgC/AFDM/day to compare to suberkropp, values are in same ballpark


# Convert to gC per day
resp_O_day<-spongedf$RespRateInd *  24 * spongedf$Post.AFDM
g_carbon_resp<-((resp_O_day* .85*(12/32)) /1000) # changes mg.O to g.C, by efficiency 0.85 * molar conversion and mg to g conversion. 

C_lost_day<-((spongedf$Pre.Dry.Weight) - ( spongedf$Post.Dry.Weight )*.3 )/ (spongedf$Days.in.Stream)

summary(lm(C_lost_day~g_carbon_resp))
plot(C_lost_day~g_carbon_resp)
abline((lm(C_lost_day~g_carbon_resp)))
abline(a=0,b=1)

plot(g_carbon_resp~spongedf$Chloride)

# convert to gC per G AFDM per day # this code is not yet correct 08/14/2020

resp_O_AFDM_day<-spongedf$RespRateInd *  24
g_carbon_AFDM_resp<-((resp_O_AFDM_day* .85*(12/32)) /1000)

lost_AFDM_day<-((spongedf$Pre.AFDM ) - ( spongedf$Post.AFDM) )/ (spongedf$Days.in.Stream)

plot(lost_AFDM_day~g_carbon_AFDM_resp)
abline(lm(lost_AFDM_day~g_carbon_AFDM_resp))
summary(lm(lost_AFDM_day~g_carbon_AFDM_resp))





```



```{r}
bResp2.models<-list()
bResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)




## Creating a vector of names to trace back models in set
bModnamesResp2 <- paste("model", 1:length(bResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = bResp2.models, modnames = bModnamesResp2, sort = TRUE)
```
=======
## Sponge Averages
 tapply(X, INDEX, FUN = NULL)
 
```{r}
 mean.resp.sponge<-tapply(spongedf$RespRateInd, spongedf$Site, mean)
 mean.break.sponge<-tapply(spongedf$Breakdown, spongedf$Site, mean)
 mean.resp.wood<-tapply(wooddf6$RespRateInd, wooddf6$Site, mean)
 mean.resp.sponge
 mean.resp.wood
 summary(lm(mean.break.sponge~mean.resp.sponge))

 plot(mean.break.sponge~mean.resp.sponge)
 abline(lm((mean.break.sponge~mean.resp.sponge), lwd="dashed"))
```


 
>>>>>>> 62d9dade6d363359a263b13a7fcff5acf11429c4


```{r}
plot(RespRateInd~H, data=spongedf)
plot(RespRateInd~Chloride, data=spongedf)
plot(H~Chloride, data=spongedf)
```








############################################################################################################################################################################


## Models for Respiration on Wood substrates for all the sites

############################################################################################################################################################################


Model selection for Wood based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 37 5 -152.01       0.00   0.48   0.48 81.94
model 18 5 -149.67       2.35   0.15   0.63 80.77
model 3  4 -147.65       4.37   0.05   0.68 78.43

#
```{r}
wResp2.models<-list()
wResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=wooddf6, REML = FALSE)

wResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=wooddf6, REML = FALSE)
wResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=wooddf6, REML = FALSE)




## Creating a vector of names to trace back models in set
wModnamesResp2 <- paste("model", 1:length(wResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wResp2.models, modnames = wModnamesResp2, sort = TRUE)
```
#


Results for Wood Models
           R2m       R2c
[37] 0.3971972 0.4174981
           R2m       R2c
[18] 0.3517558 0.4297015
           R2m       R2c
[18] 0.2300953 0.4328473

Here are best model was able to 40% of the variation in data for Wood veners when we model H and Ammonium [model 37]. 

```{r}
r.squaredGLMM(wResp2.models[[37]])
r.squaredGLMM(wResp2.models[[18]])
r.squaredGLMM(wResp2.models[[3]])
```
#

Results for Wood Model parameters:

[37]                       2.5 %       97.5 %
 .sig01           0.000000000  0.021760060
 .sigma           0.021252057  0.035681881
 (Intercept)      0.100059636  0.120075464
 scale(H)        -0.030626307 -0.009893319
 scale(Ammonium)  0.004746742  0.025480391

 [18]
                        2.5 %       97.5 %
 .sig01           0.000000000  0.025099866
 .sigma           0.021115050  0.036448496
 (Intercept)      0.099008188  0.121237632
 scale(Chloride) -0.033088800 -0.007897834
 scale(Ammonium)  0.007556713  0.032792015



Here we see a decrease in respration with increaing H+ (decreasing pH) and that Ammonium has a positive influence on respiration rate. 

```{r}
confint(wResp2.models[[37]])
confint(wResp2.models[[18]])
confint(wResp2.models[[3]])

summary(wResp2.models[[37]])

plot(wooddf6$H ~ wooddf6$Ammonium)
plot(wooddf6$RespRateInd ~ wooddf6$Ammonium)
plot(wooddf6$RespRateInd ~ wooddf6$H)
```



## No AMD below here
###############################
###############################

##
```{r}
 NAMD <- data.frame(scale(spongenoamdCS$Conductivity),
                   scale(spongenoamdCS$H),
                   scale(spongenoamdCS$DO),
                   scale(spongenoamdCS$Turbidity),
                   scale(spongenoamdCS$Temp),
                   scale(spongenoamdCS$Chloride),
                   scale(spongenoamdCS$SRP),
                   scale(spongenoamdCS$Nitrate),
                   scale(spongenoamdCS$Ammonium),
                   scale(spongenoamdCS$DIN))
 NAMD2 <- vifstep(NAMD, th = 10)
 NAMD2
```
 

Now we are going to run these models without the AMD Sites to see if we can better predict what happening.

##Sponge Respiration no AMD

Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 11 4  85.56       0.00   0.22   0.22 -38.19
model 17 5  85.68       0.13   0.21   0.43 -36.93
model 35 5  86.34       0.79   0.15   0.58 -37.26
model 25 5  86.67       1.11   0.13   0.71 -37.42
model 15 5  87.23       1.68   0.10   0.80 -37.71





```{r}
namdResp2.models<-list()
namdResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp2 <- paste("model", 1:length(namdResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp2.models, modnames = namdModnamesResp2, sort = TRUE)
```
OK with our best model with the major AMD sites removed with are now up to being able to explain 76% of the variability - that is awesome [Chloride] and we can explain a little bit more with a model that is Chloride + Nitrate 79%.

Results:
        R2m       R2c
[11] 0.7648643 0.8382834
        R2m       R2c
[17] 0.7909615 0.8385817
        R2m       R2c
[35] 0.78416 0.8385673
         R2m      R2c
[25] 0.7814848 0.839355
        R2m       R2c
[15] 0.7757044 0.8381526

```{r}
r.squaredGLMM(namdResp2.models[[11]])
r.squaredGLMM(namdResp2.models[[17]])
r.squaredGLMM(namdResp2.models[[35]])
r.squaredGLMM(namdResp2.models[[25]])
r.squaredGLMM(namdResp2.models[[15]])
```

                  2.5 %    97.5 %
 .sig01          0.2247126 0.7438975
 .sigma          0.4460929 0.7491957
 (Intercept)     1.2876771 1.9406538
 scale(Chloride) 0.8959800 1.5615374

 confint(namdResp2.models[[17]])
 Computing profile confidence intervals ...
                      2.5 %     97.5 %
 .sig01           0.0000000 0.64214181
 .sigma           0.4461521 0.74938105
 (Intercept)      1.3280125 1.90358062
 scale(Chloride)  0.8891018 1.48520905
 scale(Nitrate)  -0.5321232 0.06540803

 confint(namdResp2.models[[35]])
 Computing profile confidence intervals ...
                      2.5 %    97.5 %
 .sig01           0.0000000 0.6722872
 .sigma           0.4454911 0.7494177
 (Intercept)      1.3143448 1.9116776
 scale(H)        -0.5066070 0.1027717
 scale(Chloride)  0.9570247 1.5758489

 Computing profile confidence intervals ...
                       2.5 %    97.5 %
 .sig01            0.0000000 0.6821323
 .sigma            0.4456558 0.7473402
 (Intercept)       1.3156279 1.9224680
 scale(Turbidity) -0.1536385 0.6103038
 scale(Chloride)   0.9813086 1.7573359

 Computing profile confidence intervals ...
                      2.5 %    97.5 %
 .sig01           0.0000000 0.7031254
 .sigma           0.4462454 0.7498433
 (Intercept)      1.3031627 1.9246945
 scale(Temp)     -0.4726835 0.1733092
 scale(Chloride)  0.8782572 1.5232030

```{r}
confint(namdResp2.models[[11]])
 confint(namdResp2.models[[17]])
 confint(namdResp2.models[[35]])
 confint(namdResp2.models[[25]])
 confint(namdResp2.models[[15]])
```
Chloride alone becomes the top model when removing the amd Sites, accounting for 78% of the variation for sponge respiration. No of the other models provide much more predictive ability as the confidence intervals cross zero - however - including the variables did help the model fit. 




##Wood Respiration no AMD

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -138.44       0.00   0.10   0.10 72.70
model 8  4 -138.42       0.01   0.10   0.20 74.04
model 7  4 -137.38       1.05   0.06   0.26 73.53
model 11 4 -137.14       1.30   0.05   0.31 73.40
model 3  4 -137.00       1.43   0.05   0.35 73.33
model 2  4 -136.92       1.52   0.05   0.40 73.29
model 20 5 -136.84       1.60   0.04   0.45 74.72
model 36 5 -136.57       1.87   0.04   0.48 74.59
model 13 5 -136.56       1.87   0.04   0.52 74.59
model 17 5 -136.55       1.88   0.04   0.56 74.58

```{r}
namdResp3.models<-list()
namdResp3.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp3 <- paste("model", 1:length(namdResp3.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp3.models, modnames = namdModnamesResp3, sort = TRUE)

```

Results:
      R2m       R2c
[1]   0       0.6592007
      R2m       R2c
[8] 0.1696799 0.6598294
      R2m       R2c
[7] 0.1078057 0.6611499

```{r}
r.squaredGLMM(namdResp3.models[[1]])
r.squaredGLMM(namdResp3.models[[8]])
r.squaredGLMM(namdResp3.models[[7]])
r.squaredGLMM(namdResp3.models[[11]])
r.squaredGLMM(namdResp3.models[[3]])
r.squaredGLMM(namdResp3.models[[2]])
```

```{r}
confint(namdResp3.models[[1]])
confint(namdResp3.models[[8]])
confint(namdResp3.models[[7]])
```









##################################################################################################
# Breakdown Rates
##################################################################################################
all these models are based with lm 



#all sites
```{r}
microbd <- read.csv("for breakdown all sites.csv")

spongebd <- subset(microbd, Substrate=="Cellulose Sponge")
woodbd <- subset(microbd, Substrate=="Wood Veneer")

#all sites included
```


## Sponge Breakdown all sites

Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 9  3 -72.70       0.00   0.20   0.20 40.69
model 11 4 -71.69       1.02   0.12   0.32 42.34
model 37 4 -70.73       1.98   0.07   0.39 41.86
model 4  3 -70.02       2.68   0.05   0.45 39.34
model 2  3 -69.96       2.74   0.05   0.50 39.31

```{r}
lmBreak2_avgs<-list()
 #cBreak_avgs[[1]]  <- lm( Breakdown~  ,data=spongebd)
 lmBreak2_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=spongebd)
 lmBreak2_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=spongebd)
 lmBreak2_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=spongebd)
 lmBreak2_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=spongebd)
 lmBreak2_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=spongebd)
 lmBreak2_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=spongebd)
 lmBreak2_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=spongebd)
 lmBreak2_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=spongebd)
 lmBreak2_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=spongebd)
 lmBreak2_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=spongebd)
 
lmBreak2_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=spongebd)
lmBreak2_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=spongebd)

lmBreak2_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=spongebd)
lmBreak2_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=spongebd)
lmBreak2_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=spongebd)
lmBreak2_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=spongebd)
lmBreak2_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=spongebd)
lmBreak2_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=spongebd)
lmBreak2_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=spongebd)
lmBreak2_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=spongebd)
lmBreak2_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=spongebd)
lmBreak2_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=spongebd)
lmBreak2_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=spongebd)

 ## Creating a vector of names to trace back models in set
 ModnameslmBreak2_avgs <- paste("model", 1:length(lmBreak2_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = lmBreak2_avgs, modnames = ModnameslmBreak2_avgs, sort = TRUE)
```


```{r}
summary(lmBreak2_avgs[[9]])
summary(lmBreak2_avgs[[11]])
summary(lmBreak2_avgs[[37]])
summary(lmBreak2_avgs[[4]])
summary(lmBreak2_avgs[[2]])
```

```{r}
confint(lmBreak2_avgs[[9]])
confint(lmBreak2_avgs[[11]])
confint(lmBreak2_avgs[[37]])
confint(lmBreak2_avgs[[4]])
confint(lmBreak2_avgs[[2]])
```

```{r}
plot(spongebd$Breakdown ~ spongebd$SRP)
plot(spongebd$SRP ~ spongebd$Temp)
plot(spongebd$SRP ~ spongebd$H)
plot(spongebd$Breakdown ~ spongebd$Temp)
plot(spongebd$Breakdown ~ spongebd$H)
```



## Wood Breakdown all sites

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 25 4 -133.36       0.00   0.76   0.76 73.18
model 27 4 -128.96       4.40   0.08   0.85 70.98
model 6  3 -126.51       6.85   0.02   0.87 67.59
model 4  3 -126.33       7.03   0.02   0.89 67.50
model 8  3 -125.63       7.73   0.02   0.91 67.15

```{r}
awBreak3_avgs<-list()
 #awBreak_avgs[[1]]  <- lm( Breakdown~ (, data=woodbd)
 awBreak3_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=woodbd)
 awBreak3_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=woodbd)
 awBreak3_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=woodbd)
 awBreak3_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=woodbd)
 awBreak3_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=woodbd)
 awBreak3_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=woodbd)
 awBreak3_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=woodbd)
 awBreak3_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=woodbd)
 awBreak3_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=woodbd)
 awBreak3_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=woodbd)
 
awBreak3_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=woodbd)
awBreak3_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=woodbd)
awBreak3_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=woodbd)
awBreak3_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=woodbd)

awBreak3_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=woodbd)
awBreak3_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=woodbd)
awBreak3_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=woodbd)

awBreak3_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=woodbd)
awBreak3_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=woodbd)
awBreak3_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=woodbd)

awBreak3_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=woodbd)
awBreak3_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=woodbd)
awBreak3_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=woodbd)
awBreak3_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=woodbd)
awBreak3_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=woodbd)
awBreak3_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=woodbd)
awBreak3_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=woodbd)

awBreak3_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=woodbd)
awBreak3_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=woodbd)
awBreak3_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=woodbd)
awBreak3_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=woodbd)
awBreak3_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=woodbd)
awBreak3_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=woodbd)

awBreak3_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=woodbd)
awBreak3_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=woodbd)
awBreak3_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=woodbd)
awBreak3_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=woodbd)
awBreak3_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=woodbd)
 ## Creating a vector of names to trace back models in set
 ModnamesawBreak3_avgs <- paste("model", 1:length(awBreak3_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = awBreak3_avgs, modnames = ModnamesawBreak3_avgs, sort = TRUE)
 
```


```{r}
summary(awBreak3_avgs[[25]])
summary(awBreak3_avgs[[27]])
summary(awBreak3_avgs[[6]])
summary(awBreak3_avgs[[4]])
summary(awBreak3_avgs[[8]])
```

```{r}
confint(awBreak3_avgs[[25]])
confint(awBreak3_avgs[[27]])
confint(awBreak3_avgs[[6]])
confint(awBreak3_avgs[[4]])
confint(awBreak3_avgs[[8]])

plot(woodbd$Turbidity ~ woodbd$SRP)
plot(woodbd$Breakdown ~ woodbd$SRP)
plot(woodbd$Breakdown ~ woodbd$Turbidity)
```

```{r}
plot(Breakdown~RespRateAvg, data=spongebd)
 plot(RespRateAvg~SRP, data=spongebd)
 plot(RespRateAvg~Developed..High.Intensity, data=spongebd)
 
 plot(Breakdown~RespRateAvg, data=woodbd)
 plot(RespRateAvg~SRP, data=woodbd)
 plot(RespRateAvg~Developed..High.Intensity, data=woodbd)
```










##Breakdown Rates - no AMD
```{r}
microbreakdown <- read.csv("for breakdown noamds.csv")

spongebdnoAMD <- subset(microbreakdown, Substrate=="Cellulose Sponge")
woodbdnoAMD <- subset(microbreakdown, Substrate=="Wood Veneer")

#no amd sites included
```

## Sponge Breakdown no AMD

 Model selection based on AICc:

          K   AICc Delta_AICc AICcWt Cum.Wt    LL
 model 10 3 -55.81       0.00   0.23   0.23 32.90
 model 5  3 -54.38       1.42   0.11   0.34 32.19
 model 2  3 -54.06       1.74   0.10   0.43 32.03
 model 1  3 -54.02       1.79   0.09   0.53 32.01
 model 7  3 -53.91       1.89   0.09   0.61 31.96
 model 6  3 -53.89       1.92   0.09   0.70 31.94
 
```{r}
lmBreak_avgs<-list()
 #cBreak_avgs[[1]]  <- lm( Breakdown~  ,data=spongebdnoAMD)
 lmBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=spongebdnoAMD)
 lmBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=spongebdnoAMD)
 lmBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=spongebdnoAMD)
 lmBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=spongebdnoAMD)
 lmBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=spongebdnoAMD)
 lmBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=spongebdnoAMD)
 lmBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=spongebdnoAMD)
 lmBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=spongebdnoAMD)
 lmBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=spongebdnoAMD)
 lmBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=spongebdnoAMD)
 
lmBreak_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=spongebdnoAMD)
lmBreak_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=spongebdnoAMD)
lmBreak_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=spongebdnoAMD)

lmBreak_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=spongebdnoAMD)
lmBreak_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=spongebdnoAMD)

lmBreak_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=spongebdnoAMD)
lmBreak_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=spongebdnoAMD)

lmBreak_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=spongebdnoAMD)
lmBreak_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=spongebdnoAMD)
lmBreak_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=spongebdnoAMD)
lmBreak_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=spongebdnoAMD)
lmBreak_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=spongebdnoAMD)
lmBreak_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=spongebdnoAMD)

lmBreak_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=spongebdnoAMD)
lmBreak_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=spongebdnoAMD)
lmBreak_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=spongebdnoAMD)
lmBreak_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=spongebdnoAMD)
lmBreak_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=spongebdnoAMD)

lmBreak_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=spongebdnoAMD)
lmBreak_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=spongebdnoAMD)
lmBreak_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=spongebdnoAMD)
lmBreak_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=spongebdnoAMD)
lmBreak_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=spongebdnoAMD)

 ## Creating a vector of names to trace back models in set
 ModnameslmBreak_avgs <- paste("model", 1:length(lmBreak_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = lmBreak_avgs, modnames = ModnameslmBreak_avgs, sort = TRUE)
```
 
```{r}
summary(lmBreak_avgs[[10]])
summary(lmBreak_avgs[[5]])
summary(lmBreak_avgs[[2]])
```

```{r}
confint(lmBreak_avgs[[10]])
confint(lmBreak_avgs[[5]])
confint(lmBreak_avgs[[2]])
```






## Wood Breakdown no AMD

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 9  3 -102.26       0.00   0.35   0.35 56.13
model 37 4  -99.84       2.42   0.10   0.45 57.92
model 10 3  -98.41       3.84   0.05   0.51 54.21
model 20 4  -98.39       3.87   0.05   0.56 57.20
model 1  3  -98.29       3.97   0.05   0.60 54.14

```{r}
awBreak_avgs<-list()
 #wBreak_avgs[[1]]  <- lm( Breakdown~ (, data=woodbdnoAMD, REML = FALSE)
 awBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=woodbdnoAMD)
 awBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=woodbdnoAMD)
 awBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=woodbdnoAMD)
 awBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=woodbdnoAMD)
 awBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=woodbdnoAMD)
 awBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=woodbdnoAMD)
 awBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=woodbdnoAMD)
 awBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=woodbdnoAMD)
 awBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=woodbdnoAMD)
 awBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=woodbdnoAMD)
 
awBreak_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=woodbdnoAMD)
awBreak_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=woodbdnoAMD)
awBreak_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=woodbdnoAMD)

awBreak_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=woodbdnoAMD)
awBreak_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=woodbdnoAMD)

awBreak_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=woodbdnoAMD)
awBreak_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=woodbdnoAMD)

awBreak_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=woodbdnoAMD)
awBreak_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=woodbdnoAMD)
awBreak_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=woodbdnoAMD)
awBreak_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=woodbdnoAMD)
awBreak_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=woodbdnoAMD)
awBreak_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=woodbdnoAMD)

awBreak_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=woodbdnoAMD)
awBreak_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=woodbdnoAMD)
awBreak_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=woodbdnoAMD)
awBreak_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=woodbdnoAMD)
awBreak_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=woodbdnoAMD)

awBreak_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=woodbdnoAMD)
awBreak_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=woodbdnoAMD)
awBreak_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=woodbdnoAMD)
awBreak_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=woodbdnoAMD)
awBreak_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=woodbdnoAMD)

 
 ## Creating a vector of names to trace back models in set
 ModnamesawBreak_avgs <- paste("model", 1:length(awBreak_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = awBreak_avgs, modnames = ModnamesawBreak_avgs, sort = TRUE)
 
 
```

```{r}
summary(awBreak_avgs[[9]])
summary(awBreak_avgs[[37]])
summary(awBreak_avgs[[10]])
```

```{r}
confint(awBreak_avgs[[9]])
confint(awBreak_avgs[[37]])
confint(awBreak_avgs[[10]])
```

no AMD plots
```{r}
plot(Breakdown~RespRateAvg, data=spongebdnoAMD)
 plot(RespRateAvg~SRP, data=spongebdnoAMD)
 plot(RespRateAvg~Developed..High.Intensity, data=spongebdnoAMD)
 
 plot(Breakdown~RespRateAvg, data=woodbdnoAMD)
 plot(RespRateAvg~SRP, data=woodbdnoAMD)
 plot(RespRateAvg~Developed..High.Intensity, data=woodbdnoAMD)
```


<<<<<<< HEAD
## Wood and Sponge Averages for breakdown vs resp

=======





####################################
####################################
## O2 to carbon and breakdown
####################################
####################################


#Sponge
```{r}
mean.resp.sponge<-tapply(spongedf$RespRateInd, spongedf$Site, mean)
mean.break.sponge<-tapply(spongedf$Breakdown, spongedf$Site, mean)

summary(lm(mean.break.sponge~mean.resp.sponge))

plot(( mean.break.sponge)~(mean.resp.sponge))
abline(lm((mean.break.sponge~mean.resp.sponge), lwd="dashed"))


# Convert to C
Csresp<-mean.resp.sponge*.85/24
Csbreak<-mean.break.sponge*.30

plot(Csbreak~Csresp)
abline(lm(Csbreak~Csresp))
summary(lm(Csbreak~Csresp))
```



#Wood
```{r}
mean.resp.wood<-tapply(wooddf6$RespRateInd, wooddf6$Site, mean)
mean.break.wood<-tapply(wooddf6$Breakdown, wooddf6$Site, mean)

summary(lm(mean.break.wood~mean.resp.wood))

plot(( mean.break.wood)~(mean.resp.wood))
abline(lm((mean.break.wood~mean.resp.wood), lwd="dashed"))


# Convert to C
Cwresp<-mean.resp.wood*.85/24
Cwbreak<-mean.break.wood*.45

plot(Cwbreak~Cwresp)
abline(lm(Cwbreak~Cwresp))
summary(lm(Cwbreak~Cwresp))
```




#For Sponge resp C vs breakdown C
```{r}
# Convert to gC per day
resp_O_day<-spongedf$RespRateInd *  24 * spongedf$Post.AFDM
g_carbon_resp<-((resp_O_day* .85*(12/32)) /1000) # changes mg.O to g.C, by efficiency 0.85 * molar conversion and mg to g conversion. 

C_lost_day<-((spongedf$Pre.Dry.Weight) - ( spongedf$Post.Dry.Weight )*.3 )/ (spongedf$Days.in.Stream)

summary(lm(C_lost_day~g_carbon_resp))
plot(C_lost_day~g_carbon_resp)
abline((lm(C_lost_day~g_carbon_resp)))
abline(a=0,b=1)

plot(g_carbon_resp~spongedf$Chloride)

# convert to gC per G AFDM per day # this code is not yet correct 08/14/2020
resp_O_AFDM_day<-spongedf$RespRateInd *  24
g_carbon_AFDM_resp<-((resp_O_AFDM_day* .85*(12/32)) /1000)

lost_AFDM_day<-((spongedf$Pre.AFDM ) - ( spongedf$Post.AFDM) )/ (spongedf$Days.in.Stream)

plot(lost_AFDM_day~g_carbon_AFDM_resp)
abline(lm(lost_AFDM_day~g_carbon_AFDM_resp))
summary(lm(lost_AFDM_day~g_carbon_AFDM_resp))
```

#For Wood resp C vs breakdown C
>>>>>>> 62d9dade6d363359a263b13a7fcff5acf11429c4
```{r}
# Convert to gC per day
Wresp_O_day<-wooddf4$RespRateInd *  24 * wooddf4$Post.AFDM
Wg_carbon_resp<-((Wresp_O_day* .85*(12/32)) /1000)

WC_lost_day<-((wooddf4$Pre.Dry.Weight * 0.45 ) - ( wooddf4$Post.Dry.Weight * 0.45) )/ (wooddf4$Days.in.Stream)

#Wood at week 6
W6resp_O_day<-wooddf6$RespRateInd *  24 * wooddf6$Post.AFDM
W6g_carbon_resp<-((W6resp_O_day* .85*(12/32)) /1000)

W6C_lost_day<-((wooddf6$Pre.Dry.Weight * 0.45 ) - ( wooddf6$Post.Dry.Weight * 0.45) )/ (wooddf6$Days.in.Stream)

plot(WC_lost_day~Wg_carbon_resp, xlim=c(0,.005), ylim=c(-0.002,0.013), pch=19)
#points(W6C_lost_day~W6g_carbon_resp, pch=2)
points(C_lost_day~g_carbon_resp)
#abline((lm(C_lost_day~g_carbon_resp)))
abline(a=0,b=1)

<<<<<<< HEAD

# convert to gC per G AFDM per day

=======
# convert to gC per G AFDM per day
>>>>>>> 62d9dade6d363359a263b13a7fcff5acf11429c4
Wresp_O_AFDM_day<-wooddf4$RespRateInd *  24
Wg_carbon_AFDM_resp<-((Wresp_O_AFDM_day* .85*(12/32)) /1000)

W_lost_AFDM_day<-((wooddf4$Pre.AFDM ) - ( wooddf4$Post.AFDM) )/ (wooddf4$Days.in.Stream)

plot(W_lost_AFDM_day~Wg_carbon_AFDM_resp, pch=19, xlim=c(0,.06), ylim=c(-0.01, 0.01))
points(lost_AFDM_day~g_carbon_AFDM_resp)
#abline(lm(W_lost_AFDM_day~Wg_carbon_AFDM_resp))
abline(a=0,b=1)
<<<<<<< HEAD
summary(lm(WC_lost_AFDM_day~Wg_carbon_AFDM_resp))
```
```


Graphs test for compairson with Usher and other papers
``` {r}
plot(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$SRP, ylim=c(0,7))
points(spongenoamdCS$SRP, spongenoamdCS$RespRateInd, pch=19)

summary(lm.sp.resp.srp<-(lm(spongenoamdCS$RespRateInd~spongenoamdCS$SRP)))
summary(lm(woodnoamdCS.4$SRP~woodnoamdCS.4$RespRateInd))


plot(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$DIN, ylim=c(0,7))
points(spongenoamdCS$DIN, spongenoamdCS$RespRateInd, pch=19)


plot(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$Nitrate, ylim=c(0,7))
points(spongenoamdCS$Nitrate, spongenoamdCS$RespRateInd, pch=19)

plot(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$Ammonium, ylim=c(0,7))
points(spongenoamdCS$Ammonium, spongenoamdCS$RespRateInd, pch=19)

plot(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$Chloride, ylim=c(0,7))
points(spongenoamdCS$Chloride, spongenoamdCS$RespRateInd, pch=19)

summary(lm(woodnoamdCS.4$RespRateInd~woodnoamdCS.4$Chloride, ylim=c(0,7)))


```

tapply( spongedf$RespRateInd, spongedf$Site, mean)
=======
summary(lm(W_lost_AFDM_day~Wg_carbon_AFDM_resp))

```













#### Plots
```{r}
plot(RespRateInd~Chloride, data=spongedf)
abline(lm(RespRateInd~Chloride, data=spongedf))
points(RespRateInd~Chloride, data=wooddf6, pch=16)
abline(lm(RespRateInd~Chloride, data=wooddf6))

plot(RespRateInd~SRP, data=spongedf)
abline(lm(RespRateInd~SRP, data=spongedf))
points(RespRateInd~SRP, data=wooddf6, pch=16)
abline(lm(RespRateInd~SRP, data=wooddf6))

plot(RespRateAvg~Breakdown, data=spongedf)
abline(lm(RespRateAvg~Breakdown, data=spongedf))

plot(RespRateAvg~Breakdown, data=wooddf6)
abline(lm(RespRateAvg~Breakdown, data=wooddf6))
```


mean in ggplot with error bars for resp and breakdown



```{r}
graphs <- read.csv("for graphs fig 1.csv")

substrate <- levels(graphs$Substrate)
mean <- NULL
SE <- NULL
for(i in substrate){
  # This will calculate a mean for each subset (site)
  mean[[i]] <- mean(subset(graphs, Site == i)$RespRateInd)
  # This will calculate a standard error for each subset (site)
  SE[[i]] <- sd(subset(graphs, Site == i)$RespRateInd) /
    sqrt(as.numeric(length(substrate)))
}

Graph <- data.frame(Substrate = substrate, 
                       RespRateInd = mean,
                       RespRateSE = SE)

ggplot(data = Graph, aes(x = Chloride, y = RespRateInd, fill = Substrate)) +
  geom_point() +
  geom_errorbar(aes(ymin = RespRateInd - RespRateSE,
                    ymax = RespRateInd + RespRateSE))

```




```{r}

microplot <- read.csv("fig 1 graph.csv")
 
ggplot(data = microplot, aes(x = Chloride, y = RespRateInd, col = Substrate)) +
  geom_point() +
  geom_errorbar( aes(ymin = RespRateInd-sd, ymax = +sd))

plot()
```


















>>>>>>> 62d9dade6d363359a263b13a7fcff5acf11429c4

