---
title: "Emily’s Respiration and Breakdown Data"
author: "Emily Huff and James Wood"
date: "July 15, 2020"
output: html_document
---

Starting here - 

Loading data files for the whole data set and for the NO AMD (including no Crap Stream)

```{r}

microdf <- read.csv("Emily Data.csv")
microdfa <- read.csv("Emily Data.csv")

# this removed a big outlier data point (365) - a respiraton measurement of 8 (woodsdale creek) when rest were ~1 or 2. Will need to recalculate Site average if used. Also removed  (319) which had a resp about double the others at the Site. 
microdf<-microdfa[-c(103,243,319,346, 348, 365), ]


spongedf <- subset(microdf, Substrate=="Cellulose Sponge" & Week.Removed==4)
wooddf <- subset(microdf, Substrate=="Wood Veneer" & Week.Removed==6)

```

Instead of using this new CSV, I'm going to just make a new matrix that is based on microdf but with the AMD and CS in it

```{r}
micronoamdCS<-microdf[-c(65:126, 224:253),]

spongenoamdCS <- subset(micronoamdCS, Substrate=="Cellulose Sponge" & Week.Removed==4)
woodnoamdCS <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==6)
```


Loading Libraries
```{r}
library(lme4)
library(ggplot2)
library(ggmap)
library(AICcmodavg)
library(scatterplot3d)
library(devtools)
library(cowplot)
library(MuMIn)
library(usdm)
```

Looking for colinearity in the predictor variables using VIFSTEP function.

Result: VIF score indicates DIN and conductivity has a collinearity problem,
and need to be removed from the data set if used in conjunction with other variables. We can still use them indicidually. 
```{r}
cs1 <- data.frame(scale(microdf$Conductivity),
                  scale(microdf$H),
                  scale(microdf$DO),
                  scale(microdf$Turbidity),
                  scale(microdf$Temp),
                  scale(microdf$Chloride),
                  scale(microdf$SRP),
                  scale(microdf$Nitrate),
                  scale(microdf$Ammonium),
                  scale(microdf$DIN))
cs2 <- vifstep(cs1, th = 10)
cs2
```



## This will plot the x~y relationship of all the variables. 

Result: From looking at these gaphs you can see why the conductivity and DIN were removed. DIN appears to be strongly correlated with Nitrate and Ammonia - this is expected, and Conductivity and Chloride appear to be correlated. This would be expected also. DIN and Conductivity also appear to correlated with other variables. 
```{r}
pairs(~Conductivity+    H+     DO+ Turbidity+ Temp+    Chloride+      SRP+      Nitrate+         +       Ammonium+      DIN, data=spongedf)
```

Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 


Becase we only have 13 Sites in the whole data set we will later remove the AMD impacted Sites we only have 10 Sites, we really should limit the number of predictors in our model. Ideally you have at least 10 Sites for each predcitors. This is often unrealistic, but we'll limit ourselves to models with two or less predictor variables just to be a bit conservative. If need be, we can also reduce it further)

 

# Using a more limited set of models so that we are not overfitting
# This is the same set of models (i.e. water chemistry predictors) that were
# chosen to use with the sponge data. 



######################################################################################
##                        Sponge Models
#####################################################################################

Models for Respiration on Sponge substrates

#####################################################################################
#####################################################################################

I added turbidity, DO, and H to the model choices. Also I changed the random effect to Site so that we are modeling in a way that says there is variation in each Site. If we don't do it that way, then we would need to get a Site average of respiration instead of individual respiration.



## AICc Results for Sponge with all the sties
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 35 5 121.23       0.00   0.94   0.94 -54.93
model 17 5 129.19       7.96   0.02   0.96 -58.91
model 11 4 131.37      10.14   0.01   0.96 -61.24

: Note there are some errors in running these models that not all of them converged, which I will need to look into what's going on. 

```{r}
bResp2.models<-list()
bResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)




## Creating a vector of names to trace back models in set
bModnamesResp2 <- paste("model", 1:length(bResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = bResp2.models, modnames = bModnamesResp2, sort = TRUE)
```
 
## Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 
 
 Results:
           R2m       R2c
[35] 0.6198154 0.8030915
           R2m       R2c
[17] 0.4218287 0.8048477
           R2m      R2c
[11] 0.2275871 0.802891

```{r}
r.squaredGLMM(bResp2.models[[35]])
r.squaredGLMM(bResp2.models[[17]])
r.squaredGLMM(bResp2.models[[11]])
```

Lastly we see how big of an effect our predictor variables have on respiration rate. 
From Model 35

#                    2.5 %     97.5 %
.sig01           0.3293433  0.9692943
.sigma           0.4817444  0.7637504
(Intercept)      1.3644220  2.1294752
scale(H)        -2.0319719 -0.7576644
scale(Chloride)  1.1044317  2.3789479

```{r}
confint(bResp2.models[[35]])
confint(bResp2.models[[17]])
confint(bResp2.models[[11]])
```



Conclusion for Sponge Models: 
The only model that had much support was H + Chloride and we have a nice mR2 value, indicating that we were able to explain 62% of the variation in the data with this model. 
If you plot choloride and H .. plot (Chloride~H, data=spongedf) .. you can see that we have this one really low pH Site (high H) with a big difference between it and the other Sites, AND it is our really high chloride Site. 

```{r}
plot(RespRateInd~H, data=spongedf)
plot(RespRateInd~Chloride, data=spongedf)
plot(H~Chloride, data=spongedf)
```








############################################################################################################################################################################


## Models for Respiration on Wood substrates

############################################################################################################################################################################


Model selection for Wood based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 37 5 -152.01       0.00   0.48   0.48 81.94
model 18 5 -149.67       2.35   0.15   0.63 80.77
model 3  4 -147.65       4.37   0.05   0.68 78.43

#
```{r}
wResp2.models<-list()
wResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)



wResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=wooddf, REML = FALSE)




## Creating a vector of names to trace back models in set
wModnamesResp2 <- paste("model", 1:length(wResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wResp2.models, modnames = wModnamesResp2, sort = TRUE)
```
#


Results for Wood Models
           R2m       R2c
[37] 0.3971972 0.4174981
           R2m       R2c
[18] 0.3517558 0.4297015
           R2m       R2c
[18] 0.2300953 0.4328473

Here are best model was able to 40% of the variation in data for Wood veners when we model H and Ammonium [model 37]. 

```{r}
r.squaredGLMM(wResp2.models[[37]])
r.squaredGLMM(wResp2.models[[18]])
r.squaredGLMM(wResp2.models[[3]])
```
#

Results for Wood Model parameters:
[37]                       2.5 %       97.5 %
.sig01           0.000000000  0.021760060
.sigma           0.021252057  0.035681881
(Intercept)      0.100059636  0.120075464
scale(H)        -0.030626307 -0.009893319
scale(Ammonium)  0.004746742  0.025480391

[18]
                       2.5 %       97.5 %
.sig01           0.000000000  0.025099866
.sigma           0.021115050  0.036448496
(Intercept)      0.099008188  0.121237632
scale(Chloride) -0.033088800 -0.007897834
scale(Ammonium)  0.007556713  0.032792015

Here we see a decrease in respration with increaing H+ (decreasing pH) and that Ammonium has a positive influence on respiration rate. 

```{r}
confint(wResp2.models[[37]])
confint(wResp2.models[[18]])
confint(wResp2.models[[3]])
```

##
```{r}
NAMD <- data.frame(scale(spongenoamdCS$Conductivity),
                  scale(spongenoamdCS$H),
                  scale(spongenoamdCS$DO),
                  scale(spongenoamdCS$Turbidity),
                  scale(spongenoamdCS$Temp),
                  scale(spongenoamdCS$Chloride),
                  scale(spongenoamdCS$SRP),
                  scale(spongenoamdCS$Nitrate),
                  scale(spongenoamdCS$Ammonium),
                  scale(spongenoamdCS$DIN))
NAMD2 <- vifstep(NAMD, th = 10)
NAMD2
```




## No AMD below here
###############################
###############################

Now we are going to run these models without the AMD Sites to see if we can better predict what happening.

Sponge Respiration
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 11 4  85.56       0.00   0.22   0.22 -38.19
model 17 5  85.68       0.13   0.21   0.43 -36.93
model 35 5  86.34       0.79   0.15   0.58 -37.26
model 25 5  86.67       1.11   0.13   0.71 -37.42
model 15 5  87.23       1.68   0.10   0.80 -37.71




```{r}
namdResp2.models<-list()
namdResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp2 <- paste("model", 1:length(namdResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp2.models, modnames = namdModnamesResp2, sort = TRUE)
```
OK with our best model with the major AMD sites removed with are now up to being able to explain 76% of the variability - that is awesome [Chloride] and we can explain a little bit more with a model that is Chloride + Nitrate 79%.

Results:
        R2m       R2c
[11] 0.7648643 0.8382834
        R2m       R2c
[17] 0.7909615 0.8385817
        R2m       R2c
[35] 0.78416 0.8385673
         R2m      R2c
[25] 0.7814848 0.839355
        R2m       R2c
[15] 0.7757044 0.8381526

```{r}
r.squaredGLMM(namdResp2.models[[11]])
r.squaredGLMM(namdResp2.models[[17]])
r.squaredGLMM(namdResp2.models[[35]])
r.squaredGLMM(namdResp2.models[[25]])
r.squaredGLMM(namdResp2.models[[15]])
```

                  2.5 %    97.5 %
 .sig01          0.2247126 0.7438975
 .sigma          0.4460929 0.7491957
 (Intercept)     1.2876771 1.9406538
 scale(Chloride) 0.8959800 1.5615374

 confint(namdResp2.models[[17]])
 Computing profile confidence intervals ...
                      2.5 %     97.5 %
 .sig01           0.0000000 0.64214181
 .sigma           0.4461521 0.74938105
 (Intercept)      1.3280125 1.90358062
 scale(Chloride)  0.8891018 1.48520905
 scale(Nitrate)  -0.5321232 0.06540803

 confint(namdResp2.models[[35]])
 Computing profile confidence intervals ...
                      2.5 %    97.5 %
 .sig01           0.0000000 0.6722872
 .sigma           0.4454911 0.7494177
 (Intercept)      1.3143448 1.9116776
 scale(H)        -0.5066070 0.1027717
 scale(Chloride)  0.9570247 1.5758489

 Computing profile confidence intervals ...
                       2.5 %    97.5 %
 .sig01            0.0000000 0.6821323
 .sigma            0.4456558 0.7473402
 (Intercept)       1.3156279 1.9224680
 scale(Turbidity) -0.1536385 0.6103038
 scale(Chloride)   0.9813086 1.7573359

 Computing profile confidence intervals ...
                      2.5 %    97.5 %
 .sig01           0.0000000 0.7031254
 .sigma           0.4462454 0.7498433
 (Intercept)      1.3031627 1.9246945
 scale(Temp)     -0.4726835 0.1733092
 scale(Chloride)  0.8782572 1.5232030

```{r}
confint(namdResp2.models[[11]])
 confint(namdResp2.models[[17]])
 confint(namdResp2.models[[35]])
 confint(namdResp2.models[[25]])
 confint(namdResp2.models[[15]])
```
Chloride alone becomes the top model when removing the amd Sites, accounting for 78% of the variation for sponge respiration. No of the other models provide much more predictive ability as the confidence intervals cross zero - however - including the variables did help the model fit. 





## Wood Respiration

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -138.44       0.00   0.10   0.10 72.70
model 8  4 -138.42       0.01   0.10   0.20 74.04
model 7  4 -137.38       1.05   0.06   0.26 73.53
model 11 4 -137.14       1.30   0.05   0.31 73.40
model 3  4 -137.00       1.43   0.05   0.35 73.33
model 2  4 -136.92       1.52   0.05   0.40 73.29
model 20 5 -136.84       1.60   0.04   0.45 74.72
model 36 5 -136.57       1.87   0.04   0.48 74.59
model 13 5 -136.56       1.87   0.04   0.52 74.59
model 17 5 -136.55       1.88   0.04   0.56 74.58

```{r}
namdResp3.models<-list()
namdResp3.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)



namdResp3.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp3 <- paste("model", 1:length(namdResp3.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp3.models, modnames = namdModnamesResp3, sort = TRUE)

```

Results:
      R2m       R2c
[1]   0       0.6592007
      R2m       R2c
[8] 0.1696799 0.6598294
      R2m       R2c
[7] 0.1078057 0.6611499

```{r}
r.squaredGLMM(namdResp3.models[[1]])
r.squaredGLMM(namdResp3.models[[8]])
r.squaredGLMM(namdResp3.models[[7]])
r.squaredGLMM(namdResp3.models[[11]])
r.squaredGLMM(namdResp3.models[[3]])
r.squaredGLMM(namdResp3.models[[2]])
```

```{r}
confint(namdResp3.models[[1]])
confint(namdResp3.models[[8]])
confint(namdResp3.models[[7]])
```









##################################################################################################
# Breakdown Rates
##################################################################################################
No AMD


i made a new file to run the breakdown stuff in
```{r}
microbreakdown <- read.csv("for breakdown noamds.csv")

spongebdnoAMD <- subset(microbreakdown, Substrate=="Cellulose Sponge")
woodbdnoAMD <- subset(microbreakdown, Substrate=="Wood Veneer")

#These dont have any amd sites included
```

For sponge - the null model is the best model - basically we can't explain breakdown across the whole site

Sponge
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -53.46       0.00   0.56   0.56 31.73
model 11 4 -49.81       3.65   0.09   0.65 32.90
model 6  4 -48.38       5.08   0.04   0.70 32.19
model 3  4 -48.36       5.10   0.04   0.74 32.18
model 2  4 -48.11       5.35   0.04   0.78 32.06
```{r}

camdBreak_avgs<-list()
camdBreak_avgs[[1]]  <- lmer( Breakdown~ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)

camdBreak_avgs[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)

camdBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)


camdBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)


camdBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)



camdBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)

camdBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)


camdBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)
camdBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=spongebdnoAMD, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnamescamdBreak_avgs <- paste("model", 1:length(camdBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = camdBreak_avgs, modnames = ModnamescamdBreak_avgs, sort = TRUE)
#############################
```

# Breakdown with All site - what predicts breakdown on sponge?

 No need to use the LMER function here - only one number per site - Stream isn't a bad idea and we perhaps should think more about it - here is just a simple linear model 
 Model selection based on AICc:

          K   AICc Delta_AICc AICcWt Cum.Wt    LL
 model 10 3 -55.81       0.00   0.23   0.23 32.90
 model 5  3 -54.38       1.42   0.11   0.34 32.19
 model 2  3 -54.06       1.74   0.10   0.43 32.03
 model 1  3 -54.02       1.79   0.09   0.53 32.01
 model 7  3 -53.91       1.89   0.09   0.61 31.96
 model 6  3 -53.89       1.92   0.09   0.70 31.94
 
```{r}
lmBreak_avgs<-list()
 #cBreak_avgs[[1]]  <- lm( Breakdown~  ,data=spongebdnoAMD, REML = FALSE)
 lmBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=spongebdnoAMD)
 lmBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=spongebdnoAMD)
 lmBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=spongebdnoAMD)
 lmBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=spongebdnoAMD)
 lmBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=spongebdnoAMD)
 lmBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=spongebdnoAMD)
 lmBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=spongebdnoAMD)
 lmBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=spongebdnoAMD)
 lmBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=spongebdnoAMD)
 lmBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=spongebdnoAMD)
 
lmBreak_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[15]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=spongebdnoAMD, REML = FALSE)

lmBreak_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[18]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)

lmBreak_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[20]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[21]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)

lmBreak_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[28]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)

lmBreak_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale (H), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[34]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)

lmBreak_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=spongebdnoAMD, REML = FALSE)
lmBreak_avgs[[39]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=spongebdnoAMD, REML = FALSE)

 ## Creating a vector of names to trace back models in set
 ModnameslmBreak_avgs <- paste("model", 1:length(lmBreak_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = lmBreak_avgs, modnames = ModnameslmBreak_avgs, sort = TRUE)
```
 
```{r}
r.squaredGLMM(lmBreak_avgs[[10]])
```






Wood
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -97.16       0.00   0.43   0.43 53.58
model 10 4 -96.26       0.90   0.27   0.70 56.13
model 11 4 -92.41       4.75   0.04   0.74 54.21
model 2  4 -92.29       4.87   0.04   0.78 54.14
model 4  4 -91.98       5.18   0.03   0.81 53.99

```{r}
wamdBreak_avg<-list()
wamdBreak_avg[[1]]  <- lmer( Breakdown~ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)

wamdBreak_avg[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)

wamdBreak_avg[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)


wamdBreak_avg[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)


wamdBreak_avg[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)



wamdBreak_avg[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)

wamdBreak_avg[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)


wamdBreak_avg[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)
wamdBreak_avg[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=woodbdnoAMD, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnameswamdBreak_avg <- paste("model", 1:length(wamdBreak_avg), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wamdBreak_avg, modnames = ModnameswamdBreak_avg, sort = TRUE)
```


Here is just used a simple linear model to for breakdown because we only have one number for each site. We could try to run as LMER with the random effect of "stream" but when I did that I had a lot of 'bse" errors becasue most of the sites only have one site in each stream. 

Emily - I made a quick set of models - I'd like you to update the rest of the list - models 12-39 and rerun this to see if any of them are better. 



```{r}
aawBreak_avgs<-list()
 #wBreak_avgs[[1]]  <- lm( Breakdown~ (, data=woodbdnoAMD, REML = FALSE)
 aawBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=woodbdnoAMD)
 aawBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=woodbdnoAMD)
 aawBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO), data=woodbdnoAMD)
 aawBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=woodbdnoAMD)
 aawBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp), data=woodbdnoAMD)
 aawBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN), data=woodbdnoAMD)

 aawBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate), data=woodbdnoAMD)
 aawBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium), data=woodbdnoAMD)
 aawBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=woodbdnoAMD)
 aawBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=woodbdnoAMD)
 
aawBreak_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=woodbdnoAMD)
aawBreak_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=woodbdnoAMD)
aawBreak_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=woodbdnoAMD)

aawBreak_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=woodbdnoAMD)
aawBreak_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=woodbdnoAMD)

aawBreak_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=woodbdnoAMD)
aawBreak_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=woodbdnoAMD)

aawBreak_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=woodbdnoAMD)
aawBreak_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=woodbdnoAMD)
aawBreak_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=woodbdnoAMD)
aawBreak_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=woodbdnoAMD)
aawBreak_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=woodbdnoAMD)
aawBreak_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=woodbdnoAMD)

aawBreak_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=woodbdnoAMD)
aawBreak_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=woodbdnoAMD)
aawBreak_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=woodbdnoAMD)
aawBreak_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=woodbdnoAMD)
aawBreak_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=woodbdnoAMD)

aawBreak_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=woodbdnoAMD)
aawBreak_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=woodbdnoAMD)
aawBreak_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=woodbdnoAMD)
aawBreak_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=woodbdnoAMD)
aawBreak_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=woodbdnoAMD)

 
 ## Creating a vector of names to trace back models in set
 aModnamesawBreak_avgs <- paste("model", 1:length(aawBreak_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = aawBreak_avgs, modnames = aModnamesawBreak_avgs, sort = TRUE)
 
 
```

```{r}
summary(aawBreak_avgs[[9]])
summary(aawBreak_avgs[[37]])
summary(aawBreak_avgs[[10]])

```

```{r}
confint(awBreak_avgs[[9]])
confint(awBreak_avgs[[37]])
confint(awBreak_avgs[[10]])
```

```{r}
plot(Breakdown~RespRateAvg, data=spongebdnoAMD)
 plot(RespRateAvg~SRP, data=spongebdnoAMD)
 plot(RespRateAvg~Developed..High.Intensity, data=spongebdnoAMD)
```

Emily - I'd like you to run your breakdown models with "all the sites" i.e. what is above and again with all the AMD sites removed. Then make plots of Resp vs Breakdown for all sites and resp vs breakdown for the site with AMD removed. 

The above models for breakdown already did not have any AMD sites included in them


###############
Below here i will have breakdown models that include all the sites

```{r}
microbd <- read.csv("for breakdown all sites.csv")

spongebd <- subset(microbd, Substrate=="Cellulose Sponge")
woodbd <- subset(microbd, Substrate=="Wood Veneer")
```


sponge
```{r}
cBreak_avgs<-list()
cBreak_avgs[[1]]  <- lmer( Breakdown~ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)



cBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=spongebd, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnamescBreak_avgs <- paste("model", 1:length(cBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = cBreak_avgs, modnames = ModnamescBreak_avgs, sort = TRUE)
#############################
```


# Results for Sponge Breakdown No AMD
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 9  3 -72.70       0.00   0.20   0.20 40.69
model 11 4 -71.69       1.02   0.12   0.32 42.34
model 37 4 -70.73       1.98   0.07   0.39 41.86

```{r}
lmBreak2_avgs<-list()
 #cBreak_avgs[[1]]  <- lm( Breakdown~  ,data=spongebd, REML = FALSE)
 lmBreak2_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=spongebd)
 lmBreak2_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=spongebd)
 lmBreak2_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=spongebd)
 lmBreak2_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=spongebd)
 lmBreak2_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=spongebd)
 lmBreak2_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=spongebd)
 lmBreak2_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=spongebd)
 lmBreak2_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=spongebd)
 lmBreak2_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=spongebd)
 lmBreak2_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=spongebd)
 
lmBreak2_avgs[[11]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=spongebd)
lmBreak2_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=spongebd)

lmBreak2_avgs[[15]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=spongebd)
lmBreak2_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[18]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=spongebd)
lmBreak2_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[20]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[21]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=spongebd)
lmBreak2_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=spongebd)
lmBreak2_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=spongebd)
lmBreak2_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=spongebd)
lmBreak2_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[28]]  <- lm( Breakdown~ scale(DO) + scale (H), data=spongebd)
lmBreak2_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=spongebd)
lmBreak2_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=spongebd)
lmBreak2_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=spongebd)

lmBreak2_avgs[[34]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=spongebd)
lmBreak2_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=spongebd)
lmBreak2_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=spongebd)
lmBreak2_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=spongebd)
lmBreak2_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=spongebd)

 ## Creating a vector of names to trace back models in set
 ModnameslmBreak2_avgs <- paste("model", 1:length(lmBreak2_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = lmBreak2_avgs, modnames = ModnameslmBreak2_avgs, sort = TRUE)
```


```{r}
summary(lmBreak2_avgs[[9]])
summary(lmBreak2_avgs[11])
summary(lmBreak2_avgs[[37]])
```

```{r}
confint(lmBreak2_avgs[[9]])
confint(lmBreak2_avgs[[11]])
confint(lmBreak2_avgs[[37]])

```







####################
## Breakdown on Wood all sites


wood
```{r}
wBreak_avgs<-list()
wBreak_avgs[[1]]  <- lmer( Breakdown~ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)



wBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=woodbd, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnameswBreak_avgs <- paste("model", 1:length(wBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wBreak_avgs, modnames = ModnameswBreak_avgs, sort = TRUE)
```



```{r}
awBreak3_avgs<-list()
 #wBreak_avgs[[1]]  <- lm( Breakdown~ (, data=woodbd, REML = FALSE)
 awBreak3_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=woodbd)
 awBreak3_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=woodbd)
 awBreak3_avgs[[3]]  <- lm( Breakdown~ scale(DO), data=woodbd)
 awBreak3_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=woodbd)
 awBreak3_avgs[[5]]  <- lm( Breakdown~ scale(Temp), data=woodbd)
 awBreak3_avgs[[6]]  <- lm( Breakdown~ scale(DIN), data=woodbd)

 awBreak3_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate), data=woodbd)
 awBreak3_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium), data=woodbd)
 awBreak3_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=woodbd)
 awBreak3_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=woodbd)
 
 awBreak3_avgs[[12]]  <- lm( Breakdown~ scale(Temp) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[13]]  <- lm( Breakdown~ scale(Temp) + scale(Nitrate), data=woodbd, REML = FALSE)
awBreak3_avgs[[14]]  <- lm( Breakdown~ scale(Temp) + scale(Ammonium), data=woodbd, REML = FALSE)
awBreak3_avgs[[15]]  <- lm( Breakdown~ scale(Temp) + scale(Chloride), data=woodbd, REML = FALSE)

awBreak3_avgs[[16]]  <- lm( Breakdown~ scale(Chloride) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[17]]  <- lm( Breakdown~ scale(Chloride) + scale(Nitrate), data=woodbd, REML = FALSE)
awBreak3_avgs[[18]]  <- lm( Breakdown~ scale(Chloride) + scale(Ammonium), data=woodbd, REML = FALSE)

awBreak3_avgs[[19]]  <- lm( Breakdown~ scale(Nitrate) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[20]]  <- lm( Breakdown~ scale(Nitrate) + scale(Ammonium), data=woodbd, REML = FALSE)
awBreak3_avgs[[21]]  <- lm( Breakdown~ scale(SRP) + scale(Ammonium), data=woodbd, REML = FALSE)

awBreak3_avgs[[22]]  <- lm( Breakdown~ scale(Turbidity) + scale(H), data=woodbd, REML = FALSE)
awBreak3_avgs[[23]]  <- lm( Breakdown~ scale(Turbidity) + scale(DO), data=woodbd, REML = FALSE)
awBreak3_avgs[[24]]  <- lm( Breakdown~ scale(Turbidity) + scale(Temp), data=woodbd, REML = FALSE)
awBreak3_avgs[[25]]  <- lm( Breakdown~ scale(Turbidity) + scale(Chloride), data=woodbd, REML = FALSE)
awBreak3_avgs[[26]]  <- lm( Breakdown~ scale(Turbidity) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[27]]  <- lm( Breakdown~ scale(Turbidity) + scale(Nitrate), data=woodbd, REML = FALSE)
awBreak3_avgs[[28]]  <- lm( Breakdown~ scale(Turbidity) + scale(Ammonium), data=woodbd, REML = FALSE)

awBreak3_avgs[[29]]  <- lm( Breakdown~ scale(DO) + scale (H), data=woodbd, REML = FALSE)
awBreak3_avgs[[30]]  <- lm( Breakdown~ scale(DO) + scale(Temp), data=woodbd, REML = FALSE)
awBreak3_avgs[[31]]  <- lm( Breakdown~ scale(DO) + scale(Chloride), data=woodbd, REML = FALSE)
awBreak3_avgs[[32]]  <- lm( Breakdown~ scale(DO) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[33]]  <- lm( Breakdown~ scale(DO) + scale(Nitrate), data=woodbd, REML = FALSE)
awBreak3_avgs[[34]]  <- lm( Breakdown~ scale(DO) + scale(Ammonium), data=woodbd, REML = FALSE)

awBreak3_avgs[[35]]  <- lm( Breakdown~ scale(H) + scale(Chloride), data=woodbd, REML = FALSE)
awBreak3_avgs[[36]]  <- lm( Breakdown~ scale(H) + scale(Nitrate), data=woodbd, REML = FALSE)
awBreak3_avgs[[37]]  <- lm( Breakdown~ scale(H) + scale(Ammonium), data=woodbd, REML = FALSE)
awBreak3_avgs[[38]]  <- lm( Breakdown~ scale(H) + scale(SRP), data=woodbd, REML = FALSE)
awBreak3_avgs[[39]]  <- lm( Breakdown~ scale(H) + scale(Temp), data=woodbd, REML = FALSE)
 
 ## Creating a vector of names to trace back models in set
 ModnamesawBreak3_avgs <- paste("model", 1:length(awBreak3_avgs), sep = " ")

 ##generate AICc table from candidate models so that you can control the model
 aictab(cand.set = awBreak3_avgs, modnames = ModnamesawBreak3_avgs, sort = TRUE)
 
```


all sites
```{r}
plot(Breakdown~RespRateAvg, data=spongebd)
 plot(RespRateAvg~SRP, data=spongebd)
 plot(RespRateAvg~Developed..High.Intensity, data=spongebd)
 
 plot(Breakdown~RespRateAvg, data=woodbd)
 plot(RespRateAvg~SRP, data=woodbd)
 plot(RespRateAvg~Developed..High.Intensity, data=woodbd)
```


no AMD
```{r}
plot(Breakdown~RespRateAvg, data=spongebdnoAMD)
 plot(RespRateAvg~SRP, data=spongebdnoAMD)
 plot(RespRateAvg~Developed..High.Intensity, data=spongebdnoAMD)
 
 plot(Breakdown~RespRateAvg, data=woodbdnoAMD)
 plot(RespRateAvg~SRP, data=woodbdnoAMD)
 plot(RespRateAvg~Developed..High.Intensity, data=woodbdnoAMD)
```

