---
title: "Emily’s Respiration and Breakdown Data"
author: "Emily Huff and James Wood"
date: "July 15, 2020"
output: html_document
---

Starting here - 

Loading data files for the whole data set and for the NO AMD (including no Crap Stream)

```{r}

microdf <- read.csv("Emily Data.csv")

microdfa <- read.csv("Emily Data.csv")

# this removed a big outlier data point (365) - a respiraton measurement of 8 (woodsdale creek) when rest were ~1 or 2. Will need to recalculate Site average if used. Also removed  (319) which had a resp about double the others at the Site. 
microdf<-microdfa[-c(103,243,319,346, 348, 365), ]
```


```{r}
spongedf <- subset(microdf, Substrate=="Cellulose Sponge" & Week.Removed==4)
wooddf <- subset(microdf, Substrate=="Wood Veneer" & Week.Removed==6)
```

Instead of using this new CSV, I'm going to just make a new matrix that is based on microdf but with the AMD and CS in it

```{r}
micronoamdCS<-microdf[-c(65:126, 224:253),]
```

```{r}
#micronoamdCS <- read.csv("Emily Data No AMD or CS.csv")

spongenoamdCS <- subset(micronoamdCS, Substrate=="Cellulose Sponge" & Week.Removed==4)
woodnoamdCS <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==6)
```

```{r}
#i removed the same outliers in this group also
#micronoamdCSa <- read.csv("Emily Data No AMD or CS.csv")

#micronoamdCS<-micronoamdCSa[-c(224, 251, 253, 270), ]

#spongenoamdCS <- subset(micronoamdCS, Substrate=="Cellulose Sponge" & Week.Removed==4)
#woodnoamdCS <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==6)
```




Loading Libraries
```{r}
library(lme4)
library(ggplot2)
library(ggmap)
library(AICcmodavg)
library(scatterplot3d)
library(devtools)
library(cowplot)
library(MuMIn)
library(usdm)
```

=======
>>>>>>> 68afcd91530453fec18a091821858c00a9d7164b
```

Looking for colinearity in the predictor variables using VIFSTEP function.

Result: VIF score indicates DIN and conductivity has a collinearity problem,
and need to be removed from the data set if used in conjunction with other variables. We can still use them indicidually. 
```{r}
cs1 <- data.frame(scale(microdf$Conductivity),
                  scale(microdf$H),
                  scale(microdf$DO),
                  scale(microdf$Turbidity),
                  scale(microdf$Temp),
                  scale(microdf$Chloride),
                  scale(microdf$SRP),
                  scale(microdf$Nitrate),
                  scale(microdf$Ammonium),
                  scale(microdf$DIN))
cs2 <- vifstep(cs1, th = 10)
cs2
```



# This will plot the x~y relationship of all the variables. 

Result: From looking at these gaphs you can see why the conductivity and DIN were removed. DIN appears to be strongly correlated with Nitrate and Ammonia - this is expected, and Conductivity and Chloride appear to be correlated. This would be expected also. DIN and Conductivity also appear to correlated with other variables. 
```{r}
pairs(~Conductivity+    H+     DO+ Turbidity+ Temp+    Chloride+      SRP+      Nitrate+         +       Ammonium+      DIN, data=spongedf)
```

Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 


<<<<<<< HEAD
Becase we only have 13 sites in the whole data set we will later remove the AMD impacted sites we only have 10 sites, we really should limit the number of predictors in our model. Ideally you have at least 10 sites for each predcitors. This is often unrealistic, but we'll limit ourselves to models with two or less predictor variables just to be a bit conservative. If need be, we can also reduce it further)
=======
Becase we only have 13 Sites in the whole data set we will later remove the AMD impacted Sites we only have 10 Sites, we really should limit the number of predictors in our model. Ideally you have at least 10 Sites for each predcitors. This is often unrealistic, but we'll limit ourselves to models with two or less predictor variables just to be a bit conservative. If need be, we can also reduce it further)
>>>>>>> 68afcd91530453fec18a091821858c00a9d7164b

 

# Using a more limited set of models so that we are not overfitting
# This is the same set of models (i.e. water chemistry predictors) that were
# chosen to use with the sponge data. 



<<<<<<< HEAD
###############################################################################################
###############################################################################################

Models for Respiration on Sponge substrates

###############################################################################################

I added turbidity, DO, and H to the model choices. Also I changed the random effect to Site so that we are modeling in a way that says there is variation in each site. If we don't do it that way, then we would need to get a site average of respiration instead of individual respiration.



Results: Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 35 5 172.50       0.00   0.94   0.94 -80.58
model 17 5 181.29       8.79   0.01   0.95 -84.98
model 11 4 182.83      10.33   0.01   0.96 -86.98
=======
######################################################################################
                        Sponge Models
#####################################################################################

Models for Respiration on Sponge substrates

#####################################################################################
#####################################################################################

I added turbidity, DO, and H to the model choices. Also I changed the random effect to Site so that we are modeling in a way that says there is variation in each Site. If we don't do it that way, then we would need to get a Site average of respiration instead of individual respiration.



AICc Results for Sponge 
Model selection based on AICc:


         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 35 5 172.50       0.00   0.94   0.94 -80.58
model 17 5 181.29       8.79   0.01   0.95 -84.98
model 11 4 182.83      10.33   0.01   0.96 -86.98

: Note there are some errors in running these models that not all of them converged, which I will need to look into what's going on. 

```{r}
bResp2.models<-list()
bResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongedf, REML = FALSE)



bResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)


bResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongedf, REML = FALSE)


bResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)

bResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)


bResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongedf, REML = FALSE)
bResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongedf, REML = FALSE)




## Creating a vector of names to trace back models in set
bModnamesResp2 <- paste("model", 1:length(bResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = bResp2.models, modnames = bModnamesResp2, sort = TRUE)
```
 
 Here we see how well the different models fit the data. Remember that AIC only says what is the top model, here we are able to see how well models fit the data. 

Results
           R2m       R2c
[1,] 0.4712246 0.5306029
           R2m       R2c
[1,] 0.2844836 0.5387668
           R2m       R2c
[1,] 0.1463665 0.5370639


```{r}
r.squaredGLMM(bResp2.models[[35]])
r.squaredGLMM(bResp2.models[[17]])
r.squaredGLMM(bResp2.models[[11]])
```

Lastly we see how big of an effect our predictor variables have on respiration rate. 
From Model 35
                     2.5 %     97.5 %
.sig01           0.0000000  0.9372557
.sigma           0.9026332  1.4248560
(Intercept)      1.4850883  2.2998680
scale(H)        -2.1998751 -0.8447089
scale(Chloride)  1.1523261  2.5057583

Model 17
                     2.5 %      97.5 %
.sig01           0.3866908  1.43880421
.sigma           0.8973141  1.40969053
(Intercept)      1.3130870  2.47796610
scale(Chloride)  0.2384631  1.52298092
scale(Nitrate)  -1.3042828 -0.01569123

```{r}
confint(bResp2.models[[35]])
confint(bResp2.models[[17]])
confint(bResp2.models[[11]])
```

<<<<<<< HEAD
Conclusion: 
The only model that had much support was Chloride + H and we have a pretty good mR2 value, indicating that we were able to explain 47% of the variation in the data with this model. 
If you plot choloride and H .. plot (Chloride~H, data=spongedf) .. you can see that we have this one really low pH site (high H) with a big difference between it and the other sites, AND it is our really high chloride site. 









###############################################################################################
###############################################################################################

Models for Respiration on Sponge substrates

###############################################################################################
=======


Conclusion for Sponge Models: 
The only model that had much support was H + Chloride and we have a nice mR2 value, indicating that we were able to explain 62% of the variation in the data with this model. 
If you plot choloride and H .. plot (Chloride~H, data=spongedf) .. you can see that we have this one really low pH Site (high H) with a big difference between it and the other Sites, AND it is our really high chloride Site. 

```{r}
plot(RespRateInd~H, data=spongedf)
plot(RespRateInd~Chloride, data=spongedf)
plot(H~Chloride, data=spongedf)
```








Now running the models with Wood






Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 36 5 -138.80       0.00   0.34   0.34 75.31
model 37 5 -135.66       3.15   0.07   0.41 73.74


=======

############################################################################################################################################################################


Models for Respiration on Wood substrates

############################################################################################################################################################################


Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 36 5 -138.80       0.00   0.34   0.34 75.31
model 37 5 -135.66       3.15   0.07   0.41 73.74
model 18 5 -135.48       3.33   0.06   0.47 73.65
model 29 5 -135.33       3.47   0.06   0.53 73.57
model 3  4 -135.20       3.60   0.06   0.58 72.1


```{r}
wResp2.models<-list()
wResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=wooddf, REML = FALSE)



wResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)

wResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)


wResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=wooddf, REML = FALSE)
wResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=wooddf, REML = FALSE)




## Creating a vector of names to trace back models in set
wModnamesResp2 <- paste("model", 1:length(wResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wResp2.models, modnames = wModnamesResp2, sort = TRUE)
```


Model Fit

           R2m      R2c
[1,] 0.3492535 0.436603
           R2m       R2c
[1,] 0.2724751 0.4354839
           R2m       R2c
[1,] 0.2674541 0.4354107

Here are best model was able to 35% of the variation in data for Wood veners. 

```{r}
r.squaredGLMM(wResp2.models[[36]])
r.squaredGLMM(wResp2.models[[37]])
r.squaredGLMM(wResp2.models[[18]])
```


Results:
Computing profile confidence intervals ...
                      2.5 %      97.5 %
.sig01          0.000000000  0.03049484
.sigma          0.025658538  0.04394110
(Intercept)     0.100450243  0.12742971
scale(H)       -0.044666162 -0.01312626
scale(Nitrate)  0.005343637  0.03688354

                       2.5 %      97.5 %
.sig01           0.000000000  0.03573602
.sigma           0.025658538  0.04438554
(Intercept)      0.098715084  0.12916487
scale(H)        -0.036875107 -0.00539525
scale(Ammonium) -0.001821045  0.02965881

                      2.5 %       97.5 %
.sig01           0.000000000  0.036052084
.sigma           0.025658538  0.044389186
(Intercept)      0.098608675  0.129271275
scale(Chloride) -0.040208812 -0.005520347
scale(Ammonium)  0.002537053  0.037225518


Here we see a decrease in respration with increaing H+ (decreasing pH) and that nitrogen has a positive influence on respiration rate. 

```{r}
confint(wResp2.models[[36]])
confint(wResp2.models[[37]])
confint(wResp2.models[[18]])
```


Now you should run these model throug the revised breakdown data and then run it all through the NOAMDCS model. 
=======
#


#Results for Wood Models
           R2m       R2c
[37] 0.3971972 0.4174981
           R2m       R2c
[18] 0.3517558 0.4297015
           R2m       R2c
[18] 0.2300953 0.4328473

Here are best model was able to 40% of the variation in data for Wood veners when we model H and Ammonium [model 37]. 

#```{r}
r.squaredGLMM(wResp2.models[[37]])
r.squaredGLMM(wResp2.models[[18]])
r.squaredGLMM(wResp2.models[[3]])
#```
#

Results for Wood Model parameters:
                       2.5 %       97.5 %
.sig01           0.000000000  0.021760060
.sigma           0.021252057  0.035681881
(Intercept)      0.100059636  0.120075464
scale(H)        -0.030626307 -0.009893319
scale(Ammonium)  0.004746742  0.025480391


Here we see a decrease in respration with increaing H+ (decreasing pH) and that Ammonium has a positive influence on respiration rate. 

```{r}
confint(wResp2.models[[37]])
confint(wResp2.models[[18]])
confint(wResp2.models[[3]])
```



No AMD below here
###############################
###############################

Now we are going to run these models without the AMD Sites to see if we can better predict what happening.

Sponge Respiration
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 11 4  85.56       0.00   0.22   0.22 -38.19
model 17 5  85.68       0.13   0.21   0.43 -36.93
model 35 5  86.34       0.79   0.15   0.58 -37.26
model 25 5  86.67       1.11   0.13   0.71 -37.42
model 15 5  87.23       1.68   0.10   0.80 -37.71


No Errors or Boundary Singularity issues
         K   AICc Delta_AICc AICcWt Cum.Wt     LL
model 11 4  85.56       0.00   0.22   0.22 -38.19
model 17 5  85.68       0.13   0.21   0.43 -36.93
model 35 5  86.34       0.79   0.15   0.58 -37.26
model 25 5  86.67       1.11   0.13   0.71 -37.42
model 15 5  87.23       1.68   0.10   0.80 -37.71
model 31 5  87.98       2.42   0.07   0.87 -38.08
model 16 5  88.16       2.61   0.06   0.93 -38.17
```{r}
namdResp2.models<-list()
namdResp2.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=spongenoamdCS, REML = FALSE)


namdResp2.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)


namdResp2.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=spongenoamdCS, REML = FALSE)



namdResp2.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)

namdResp2.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)


namdResp2.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=spongenoamdCS, REML = FALSE)
namdResp2.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=spongenoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp2 <- paste("model", 1:length(namdResp2.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp2.models, modnames = namdModnamesResp2, sort = TRUE)
```

OK with our best model with the major AMD sites removed with are now up to being able to explain 76% of the variability - that is awesome [Chloride] and we can explain a little bit more with a model that is Chloride + Nitrate 79%.

Results:
        R2m       R2c
[11] 0.7648643 0.8382834  ok 
        R2m       R2c
[17] 0.7909615 0.8385817
        R2m       R2c
[35] 0.78416 0.8385673
          R2m      R2c
[25] 0.7814848 0.839355
           R2m       R2c
[15] 0.7757044 0.8381526

```{r}
r.squaredGLMM(namdResp2.models[[11]])
r.squaredGLMM(namdResp2.models[[17]])
r.squaredGLMM(namdResp2.models[[35]])
r.squaredGLMM(namdResp2.models[[25]])
r.squaredGLMM(namdResp2.models[[15]])

```


                  2.5 %    97.5 %
.sig01          0.2247126 0.7438975
.sigma          0.4460929 0.7491957
(Intercept)     1.2876771 1.9406538
scale(Chloride) 0.8959800 1.5615374

confint(namdResp2.models[[17]])
Computing profile confidence intervals ...
                     2.5 %     97.5 %
.sig01           0.0000000 0.64214181
.sigma           0.4461521 0.74938105
(Intercept)      1.3280125 1.90358062
scale(Chloride)  0.8891018 1.48520905
scale(Nitrate)  -0.5321232 0.06540803

confint(namdResp2.models[[35]])
Computing profile confidence intervals ...
                     2.5 %    97.5 %
.sig01           0.0000000 0.6722872
.sigma           0.4454911 0.7494177
(Intercept)      1.3143448 1.9116776
scale(H)        -0.5066070 0.1027717
scale(Chloride)  0.9570247 1.5758489

Computing profile confidence intervals ...
                      2.5 %    97.5 %
.sig01            0.0000000 0.6821323
.sigma            0.4456558 0.7473402
(Intercept)       1.3156279 1.9224680
scale(Turbidity) -0.1536385 0.6103038
scale(Chloride)   0.9813086 1.7573359

Computing profile confidence intervals ...
                     2.5 %    97.5 %
.sig01           0.0000000 0.7031254
.sigma           0.4462454 0.7498433
(Intercept)      1.3031627 1.9246945
scale(Temp)     -0.4726835 0.1733092
scale(Chloride)  0.8782572 1.5232030

```{r}
confint(namdResp2.models[[11]])
confint(namdResp2.models[[17]])
confint(namdResp2.models[[35]])
confint(namdResp2.models[[25]])
confint(namdResp2.models[[15]])
```

Chloride alone becomes the top model when removing the amd Sites, accounting for 78% of the variation for sponge respiration. No of the other models provide much more predictive ability as the confidence intervals cross zero - however - including the variables did help the model fit. 





Wood Respiration
Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -138.44       0.00   0.10   0.10 72.70
model 8  4 -138.42       0.01   0.10   0.20 74.04
model 7  4 -137.38       1.05   0.06   0.26 73.53
model 11 4 -137.14       1.30   0.05   0.31 73.40
model 3  4 -137.00       1.44   0.05   0.35 73.33
model 2  4 -136.92       1.52   0.05   0.40 73.29
model 20 5 -136.84       1.60   0.04   0.45 74.72
model 36 5 -136.57       1.87   0.04   0.48 74.59
model 13 5 -136.56       1.87   0.04   0.52 74.59
model 17 5 -136.55       1.88   0.04   0.56 74.58


```{r}
namdResp3.models<-list()
namdResp3.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=woodnoamdCS, REML = FALSE)



namdResp3.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)

namdResp3.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)


namdResp3.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=woodnoamdCS, REML = FALSE)
namdResp3.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=woodnoamdCS, REML = FALSE)




## Creating a vector of names to trace back models in set
namdModnamesResp3 <- paste("model", 1:length(namdResp3.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = namdResp3.models, modnames = namdModnamesResp3, sort = TRUE)

```

Results:
      R2m       R2c
[1]   0       0.6592007
      R2m       R2c
[8] 0.1696799 0.6598294
      R2m       R2c
[7] 0.1078057 0.6611499

```{r}
r.squaredGLMM(namdResp3.models[[1]])
r.squaredGLMM(namdResp3.models[[8]])
r.squaredGLMM(namdResp3.models[[7]])
```

```{r}
confint(namdResp3.models[[1]])
confint(namdResp3.models[[8]])
confint(namdResp3.models[[7]])
```


##################################################################################################
Breakdown
##################################################################################################
No AMD

i made a new file to run the breakdown stuff in
```{r}
microbreakdown <- read.csv("for breakdown noamds.csv")

spongebd <- subset(microbreakdown, Substrate=="Cellulose Sponge")
woodbd <- subset(microbreakdown, Substrate=="Wood Veneer")
```

For sponge - the null model is the best model - basically we can't explain breakdown across the whole site

Sponge
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -53.46       0.00   0.56   0.56 31.73
model 11 4 -49.81       3.65   0.09   0.65 32.90
model 6  4 -48.38       5.08   0.04   0.70 32.19
model 3  4 -48.36       5.10   0.04   0.74 32.18
model 2  4 -48.11       5.35   0.04   0.78 32.06
```{r}

cBreak_avgs<-list()
cBreak_avgs[[1]]  <- lmer( Breakdown~ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=spongebd, REML = FALSE)



cBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)

cBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)


cBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=spongebd, REML = FALSE)
cBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=spongebd, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnamescBreak_avgs <- paste("model", 1:length(cBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = cBreak_avgs, modnames = ModnamescBreak_avgs, sort = TRUE)
#############################
```

```{r}
r.squaredGLMM(cBreak_avgs[[10]])
```


All site - what predicts breakdown on sponge?

No need to use the LMER function here - only one number per site - Stream isn't a bad idea and we perhaps should think more about it - here is just a simple linear model 
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 10 3 -55.81       0.00   0.23   0.23 32.90
model 5  3 -54.38       1.42   0.11   0.34 32.19
model 2  3 -54.06       1.74   0.10   0.43 32.03
model 1  3 -54.02       1.79   0.09   0.53 32.01
model 7  3 -53.91       1.89   0.09   0.61 31.96
model 6  3 -53.89       1.92   0.09   0.70 31.94
```{r}
lmBreak_avgs<-list()
#cBreak_avgs[[1]]  <- lm( Breakdown~  ,data=spongebd, REML = FALSE)
lmBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=spongebd)
lmBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=spongebd)
lmBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO) , data=spongebd)
lmBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=spongebd)
lmBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp) , data=spongebd)
lmBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN) , data=spongebd)
lmBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate) , data=spongebd)
lmBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium) , data=spongebd)
lmBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=spongebd)
lmBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=spongebd)

## Creating a vector of names to trace back models in set
ModnameslmBreak_avgs <- paste("model", 1:length(lmBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = lmBreak_avgs, modnames = ModnameslmBreak_avgs, sort = TRUE)
```

```{r}
r.squaredGLMM(lmBreak_avgs[[10]])
```










Wood
Model selection based on AICc:

         K   AICc Delta_AICc AICcWt Cum.Wt    LL
model 1  3 -97.16       0.00   0.43   0.43 53.58
model 10 4 -96.26       0.90   0.27   0.70 56.13
model 11 4 -92.41       4.75   0.04   0.74 54.21
model 2  4 -92.29       4.87   0.04   0.78 54.14
model 4  4 -91.98       5.18   0.03   0.81 53.99
```{r}
wBreak_avgs<-list()
wBreak_avgs[[1]]  <- lmer( Breakdown~ (1 | Site), data=woodbd, REML = FALSE)
wBreak_avgs[[2]]  <- lmer( Breakdown~ scale(Conductivity) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[3]]  <- lmer( Breakdown~ scale(H) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[4]]  <- lmer( Breakdown~ scale(DO) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[5]]  <- lmer( Breakdown~ scale(Turbidity) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[6]]  <- lmer( Breakdown~ scale(Temp) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[7]]  <- lmer( Breakdown~ scale(DIN) + (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[8]]  <- lmer( Breakdown~ scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[9]]  <- lmer( Breakdown~ scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[10]]  <- lmer( Breakdown~ scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[11]]  <- lmer( Breakdown~ scale(Chloride) + (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)



wBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=woodbd, REML = FALSE)

## Creating a vector of names to trace back models in set
ModnameswBreak_avgs <- paste("model", 1:length(wBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = wBreak_avgs, modnames = ModnameswBreak_avgs, sort = TRUE)
```

Here is just used a simple linear model to for breakdown because we only have one number for each site. We could try to run as LMER with the random effect of "stream" but when I did that I had a lot of 'bse" errors becasue most of the sites only have one site in each stream. 

Emily - I made a quick set of models - I'd like you to update the rest of the list - models 12-39 and rerun this to see if any of them are better. 

```{r}

awBreak_avgs<-list()
#wBreak_avgs[[1]]  <- lm( Breakdown~ (, data=woodbd, REML = FALSE)
awBreak_avgs[[1]]  <- lm( Breakdown~ scale(Conductivity) , data=woodbd)
awBreak_avgs[[2]]  <- lm( Breakdown~ scale(H) , data=woodbd)
awBreak_avgs[[3]]  <- lm( Breakdown~ scale(DO), data=woodbd)
awBreak_avgs[[4]]  <- lm( Breakdown~ scale(Turbidity), data=woodbd)
awBreak_avgs[[5]]  <- lm( Breakdown~ scale(Temp), data=woodbd)
awBreak_avgs[[6]]  <- lm( Breakdown~ scale(DIN), data=woodbd)

awBreak_avgs[[7]]  <- lm( Breakdown~ scale(Nitrate), data=woodbd)
awBreak_avgs[[8]]  <- lm( Breakdown~ scale(Ammonium), data=woodbd)
awBreak_avgs[[9]]  <- lm( Breakdown~ scale(SRP) , data=woodbd)
awBreak_avgs[[10]]  <- lm( Breakdown~ scale(Chloride), data=woodbd)
```

wBreak_avgs[[12]]  <- lmer( Breakdown~ scale(Temp) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[13]]  <- lmer( Breakdown~ scale(Temp) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[14]]  <- lmer( Breakdown~ scale(Temp) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[15]]  <- lmer( Breakdown~ scale(Temp) + scale(Chloride) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[16]]  <- lmer( Breakdown~ scale(Chloride) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[17]]  <- lmer( Breakdown~ scale(Chloride) + scale(Nitrate) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[18]]  <- lmer( Breakdown~ scale(Chloride) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[19]]  <- lmer( Breakdown~ scale(Nitrate) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[20]]  <- lmer( Breakdown~ scale(Nitrate) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[21]]  <- lmer( Breakdown~ scale(SRP) + scale(Ammonium) + (1 | Stream), data=woodbd, REML = FALSE)



wBreak_avgs[[22]]  <- lmer( Breakdown~ scale(Turbidity) + scale(H)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[23]]  <- lmer( Breakdown~ scale(Turbidity) + scale(DO)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[24]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[25]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[26]]  <- lmer( Breakdown~ scale(Turbidity) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[27]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[28]]  <- lmer( Breakdown~ scale(Turbidity) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)

wBreak_avgs[[29]]  <- lmer( Breakdown~ scale(DO) + scale (H) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[30]]  <- lmer( Breakdown~ scale(DO) + scale(Temp)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[31]]  <- lmer( Breakdown~ scale(DO) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[32]]  <- lmer( Breakdown~ scale(DO) + scale(SRP)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[33]]  <- lmer( Breakdown~ scale(DO) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[34]]  <- lmer( Breakdown~ scale(DO) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)


wBreak_avgs[[35]]  <- lmer( Breakdown~ scale(H) + scale(Chloride)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[36]]  <- lmer( Breakdown~ scale(H) + scale(Nitrate)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[37]]  <- lmer( Breakdown~ scale(H) + scale(Ammonium)+ (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[38]]  <- lmer( Breakdown~ scale(H) + scale(SRP) + (1 | Stream), data=woodbd, REML = FALSE)
wBreak_avgs[[39]]  <- lmer( Breakdown~ scale(H) + scale(Temp) + (1 | Stream), data=woodbd, REML = FALSE)

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 9  3 -102.26       0.00   0.53   0.53 56.13
model 10 3  -98.41       3.84   0.08   0.60 54.21
model 1  3  -98.29       3.97   0.07   0.68 54.14
model 3  3  -97.98       4.27   0.06   0.74 53.99

```{r}
## Creating a vector of names to trace back models in set
aModnameswBreak_avgs <- paste("model", 1:length(awBreak_avgs), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = awBreak_avgs, modnames = aModnameswBreak_avgs, sort = TRUE)
```

```{r}
r.squaredGLMM(awBreak_avgs[[9]])
```
```{r}
confint(awBreak_avgs[[9]])
```

```{r}
plot(Breakdown~RespRateAvg, data=spongebd)
plot(RespRateAvg~SRP, data=spongebd)
plot(RespRateAvg~Developed..High.Intensity, data=spongebd)
```


Emily - I'd like you no run your breakdown models with "all the sites" i.e. what is above and again with all the AMD sites removed. Then make plots of Resp vs Breakdown for all sites and resp vs breakdown for the site with AMD removed. 
