---
title: "Wood week 4 stuff"
output: html_document
---
```{r}
library(lme4)
library(ggplot2)
library(ggmap)
library(AICcmodavg)
library(scatterplot3d)
library(cowplot)
library(MuMIn)
library(usdm)
```

```{r}
microdf <- read.csv("Emily Data.csv")
microdfa <- read.csv("Emily Data.csv")

microdf<-microdfa[-c(103,243,319,346, 348, 365), ]

woodweek4 <- subset(microdf, Substrate=="Wood Veneer" & Week.Removed==4)



micronoamdCS<-microdf[-c(65:126, 224:253),]

woodnoamdCSweek4 <- subset(micronoamdCS, Substrate=="Wood Veneer" & Week.Removed==4)
```

## Wood 4 respiration all sites

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 19 5 -147.51       0.00   0.26   0.26 79.66
model 20 5 -147.00       0.51   0.20   0.46 79.41
model 8  4 -145.66       1.85   0.10   0.56 77.42
model 36 5 -144.26       3.25   0.05   0.61 78.04
model 37 5 -143.62       3.88   0.04   0.65 77.72

```{r}
w4Resp4.models<-list()
w4Resp4.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=woodweek4, REML = FALSE)

w4Resp4.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=woodweek4, REML = FALSE)
w4Resp4.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=woodweek4, REML = FALSE)

## Creating a vector of names to trace back models in set
wModnamesw4Resp4 <- paste("model", 1:length(w4Resp4.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = w4Resp4.models, modnames = wModnamesw4Resp4, sort = TRUE)

```
           
  Results: 
           R2m       R2c
[19] 0.3835049 0.5205291
           R2m       R2c
[20] 0.3715095 0.5203802
           R2m       R2c
[8] 0.2587294 0.5189801
           R2m       R2c
[36] 0.2977056 0.5194638
           R2m       R2c
[37] 0.2781493 0.5192218
```{r}
r.squaredGLMM(w4Resp4.models[[19]])
r.squaredGLMM(w4Resp4.models[[20]])
r.squaredGLMM(w4Resp4.models[[8]])
r.squaredGLMM(w4Resp4.models[[36]])
r.squaredGLMM(w4Resp4.models[[37]])
```

                      2.5 %       97.5 %
.sig01          0.000000000  0.030630064
.sigma          0.022059386  0.038158264
(Intercept)     0.113990437  0.140106296
scale(Nitrate) -0.035165943 -0.008627075
scale(SRP)      0.001261925  0.027800793

                       2.5 %       97.5 %
.sig01           0.0000000000  0.031392756
.sigma           0.0220593862  0.038165748
(Intercept)      0.1137334267  0.140363307
scale(Nitrate)  -0.0375878856 -0.009968557
scale(Ammonium)  0.0002882893  0.027907618

```{r}
confint(w4Resp4.models[[19]])
confint(w4Resp4.models[[20]])
confint(w4Resp4.models[[8]])
confint(w4Resp4.models[[36]])
confint(w4Resp4.models[[37]])
```



## Wood week 4 respiration no AMD

Model selection based on AICc:

         K    AICc Delta_AICc AICcWt Cum.Wt    LL
model 4  4 -112.47       0.00   0.14   0.14 61.03
model 29 5 -112.30       0.17   0.13   0.27 62.40
model 34 5 -112.05       0.42   0.11   0.38 62.28
model 33 5 -111.27       1.20   0.08   0.46 61.89
model 30 5 -110.41       2.06   0.05   0.51 61.46


so this is better than our week 6 model the null is not the top model here DO is and the next models under the top all have an indluence of DO too

```{r}
aw4Resp5.models<-list()
aw4Resp5.models[[1]]  <- lmer( RespRateInd~ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[2]]  <- lmer( RespRateInd~ scale(Conductivity) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[3]]  <- lmer( RespRateInd~ scale(H) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[4]]  <- lmer( RespRateInd~ scale(DO) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[5]]  <- lmer( RespRateInd~ scale(Turbidity) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[6]]  <- lmer( RespRateInd~ scale(Temp) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[7]]  <- lmer( RespRateInd~ scale(DIN) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[8]]  <- lmer( RespRateInd~ scale(Nitrate) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[9]]  <- lmer( RespRateInd~ scale(Ammonium) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[10]]  <- lmer( RespRateInd~ scale(SRP) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[11]]  <- lmer( RespRateInd~ scale(Chloride) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[12]]  <- lmer( RespRateInd~ scale(Temp) + scale(SRP) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[13]]  <- lmer( RespRateInd~ scale(Temp) + scale(Nitrate) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[14]]  <- lmer( RespRateInd~ scale(Temp) + scale(Ammonium) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[15]]  <- lmer( RespRateInd~ scale(Temp) + scale(Chloride) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[16]]  <- lmer( RespRateInd~ scale(Chloride) + scale(SRP) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[17]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Nitrate) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[18]]  <- lmer( RespRateInd~ scale(Chloride) + scale(Ammonium) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[19]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(SRP) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[20]]  <- lmer( RespRateInd~ scale(Nitrate) + scale(Ammonium) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[21]]  <- lmer( RespRateInd~ scale(SRP) + scale(Ammonium) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[22]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(H)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[23]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(DO)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[24]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Temp)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[25]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Chloride)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[26]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(SRP)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[27]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Nitrate)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[28]]  <- lmer( RespRateInd~ scale(Turbidity) + scale(Ammonium)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[29]]  <- lmer( RespRateInd~ scale(DO) + scale (H) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[30]]  <- lmer( RespRateInd~ scale(DO) + scale(Temp)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[31]]  <- lmer( RespRateInd~ scale(DO) + scale(Chloride)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[32]]  <- lmer( RespRateInd~ scale(DO) + scale(SRP)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[33]]  <- lmer( RespRateInd~ scale(DO) + scale(Nitrate)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[34]]  <- lmer( RespRateInd~ scale(DO) + scale(Ammonium)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

aw4Resp5.models[[35]]  <- lmer( RespRateInd~ scale(H) + scale(Chloride)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[36]]  <- lmer( RespRateInd~ scale(H) + scale(Nitrate)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[37]]  <- lmer( RespRateInd~ scale(H) + scale(Ammonium)+ (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[38]]  <- lmer( RespRateInd~ scale(H) + scale(SRP) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)
aw4Resp5.models[[39]]  <- lmer( RespRateInd~ scale(H) + scale(Temp) + (1 | Site), data=woodnoamdCSweek4, REML = FALSE)

## Creating a vector of names to trace back models in set
wModnamesaw4Resp5 <- paste("model", 1:length(aw4Resp5.models), sep = " ")

##generate AICc table from candidate models so that you can control the model
aictab(cand.set = aw4Resp5.models, modnames = wModnamesaw4Resp5, sort = TRUE)
```

Results:
           R2m      R2c
[4] 0.2519603 0.296162
           R2m       R2c
[29] 0.3208826 0.3208826
           R2m       R2c
[34] 0.3151926 0.3151926
           R2m       R2c
[33] 0.2966426 0.2972416
           R2m      R2c
[30] 0.2750768 0.296709

```{r}
r.squaredGLMM(aw4Resp5.models[[4]])
r.squaredGLMM(aw4Resp5.models[[29]])
r.squaredGLMM(aw4Resp5.models[[34]])
r.squaredGLMM(aw4Resp5.models[[33]])
r.squaredGLMM(aw4Resp5.models[[30]])
```

                2.5 %     97.5 %
.sig01      0.000000000 0.02724837
.sigma      0.023211305 0.04160996
(Intercept) 0.115064966 0.14154667
scale(DO)   0.004925056 0.03185947

                2.5 %     97.5 %
.sig01       0.000000000 0.02232705
.sigma       0.023184238 0.03985100
(Intercept)  0.116709831 0.13990180
scale(DO)    0.006510669 0.03010007
scale(H)    -0.002123022 0.02146638
```{r}
confint(aw4Resp5.models[[4]])
confint(aw4Resp5.models[[29]])
confint(aw4Resp5.models[[34]])
confint(aw4Resp5.models[[33]])
confint(aw4Resp5.models[[30]])
```


## Week Four breakdown
Ok  - I think we are getting a better story out of the week 4 breakdown, so I think we should run with this. It is also a nice comparison since both sponge and wood are now on the same time frame. 

You'll need to recalculate breakdown rate using the week 4 data and then we'll use the same subset of models to see what the best predictors are. 

# Plot Week 4 wood No AMD
plot(RespRateInd ~ DO, data = woodnoamdCSweek4)
plot(RespRateInd ~ pH, data = woodnoamdCSweek4)

